Multiband Periodograms of Astronomical Sources

### 2014-12-11 writeup/paper.tex
add bibliography stuff to paper

\begin{itemize}
  \item Relationship between Fourier Periodogram \& Least Squares fit (cite Jaynes)
  \item Matrix form of linear models
  \item Generalization of single-term to multi-term models
  \item Show expression for Power; refer to appendix for computational details
\end{itemize}

@@

\section{Appendices}

@@

As an example of one of these generalizations, consider the {\it generalized Lomb-Scargle} method of Zechmeister [cite]. This adjusts the classic Lomb-Scargle algorithm by using a model with a floating mean, which can be more accurate for certain observing cadences:

>>>>

\begin{itemize}
  \item Relationship between Fourier Periodogram \& Least Squares fit \citep{Jaynes96}
  \item Matrix form of linear models
  \item Generalization of single-term to multi-term models
  \item Show expression for Power; refer to appendix for computational details
\end{itemize}

@@

\bibliographystyle{apj}
\bibliography{paper}

@@

As an example of one of these generalizations, consider the {\it generalized Lomb-Scargle} method of \citep{Zechmeister09}. This adjusts the classic Lomb-Scargle algorithm by using a model with a floating mean, which can be more accurate for certain observing cadences:
